---
title: "Class activity work"
code-fold: true
---

```{r}
students <- c("David", "Dibaloke", "Emily", "Tedi", "Alberto", 
              "Caldwell", "Eimienwanlan", "Edward", "Mark", "Adam", 
              "Jennifer", "Josh", "Kathryn", "Clint", "Brigida")
generate_group <- function(all, leader_can, seed, 
                           no_lead1 = 2, no_lead2 = 2, no_mem1 = 6) {
    students <- all
    set.seed(seed)
    lead1 <- sample(leader_can, no_lead1)
    students <- setdiff(students, lead1)
    leader <- setdiff(leader_can, lead1)
    set.seed(seed)
    member1 <- sample(students, no_mem1)
    students <- setdiff(students, member1)
    leader <- setdiff(leader, member1)
    set.seed(seed)
    lead2 <- sample(leader, no_lead2)
    member2 <- setdiff(students, lead2)
    return(list("G1_leader" = lead1,
                "G1_member" = member1,
                "G2_leader" = lead2,
                "G2_member" = member2,
                "leader_can" = setdiff(leader_can, c(lead1, lead2))))
}
```

## Class activity 1

::: {.callout collapse="true"}
### Topic: Bootstrapping

What is bootstrapping? Why do we use bootstrapping? Please explain it and show how it can be used in simple linear regression, including code demo.

### Resources

Course slides [Simulation-based Inference](https://math4780-f23.github.io/website/slides/11-bootstrap.html#/title-slide) could be helpful. Please collect and prepare your own materials.

```{r}
act1 <- generate_group(all = students, leader_can = students, seed = 6250)
```


### Group 1

#### [Slides](https://marq-my.sharepoint.com/:p:/g/personal/dibaloke_chanda_marquette_edu/EV8jl0O2x25Pq4WqvR11mjIBmmV04Vtigs7ygbiGlfpclg?e=8cPsz3)

#### R code [example-1](./documents/act/act1_g1_ex1.R) [example-2](./documents/act/act1_g1_ex2.R)


#### Leaders:

```{r}
#| echo: false
act1$G1_leader
```

#### Members:

```{r}
#| echo: false
act1$G1_member
```

### Group 2

#### [Slides](./documents/act1_g2.pdf)

#### Leaders:

```{r}
#| echo: false
act1$G2_leader
```

#### Members:

```{r}
#| echo: false
act1$G2_member
```

### Knowledge Check

Please go to <https://forms.office.com/r/q7MXBw3raw> to answer the knowledge check questions.

<!-- <https://forms.office.com/r/q7MXBw3raw> -->

### Evaluation

For *leaders*, please go to <https://forms.office.com/r/D2RPbi5VK2> to nominate most engaged members. Note that **you two leaders make one single decision and nominate members jointly**.

For *group members*, please go to <https://forms.office.com/r/WUCKQNJ3Sd> to evaluate your leaders' performance.
:::

## Class activity 2

### Topic: Generalized Linear Models and Generalized Additive Models

::: {.callout-tip}
Focus on the concepts and ideas, and avoid mathematical details.
:::

1. Define Generalized Linear Models (GLMs) and Generalized Additive Models (GAMs). What are their similarities and differences?

2. Why using these models? What are the main properties of the two models? What can they do but multiple linear regression can't?

3. Provide an example or special case of GLM and GAM.

4. Code demo how to run a GLM and GAM.


```{r}
#| echo: true
leader_can <- setdiff(students, c(act1$G1_leader, act1$G2_leader))
act2 <- generate_group(all = students, leader_can = leader_can, seed = 6250)
```



### Group 1

#### Leaders:

```{r}
#| echo: false
act2$G1_leader
```

#### Members:

```{r}
#| echo: false
act2$G1_member
```

### Group 2

#### Leaders:

```{r}
#| echo: false
act2$G2_leader
```

#### Members:

```{r}
#| echo: false
act2$G2_member
```


### Knowledge Check

Please go to <https://forms.office.com/r/Bt5rVJ5igB> to answer the knowledge check questions.

### Evaluation

For *leaders*, please go to <https://forms.office.com/r/Ys2rAFW8pe> to nominate most engaged members. Note that **you two leaders make one single decision and nominate members jointly**.

For *group members*, please go to <https://forms.office.com/r/tk9FrnV9ZM> to evaluate your leaders' performance.




## Class activity 3

<!-- ### Topic: Gaussian Process Classification -->

<!-- ### Topic: Artificial Neural Networks -->

<!-- ::: {.callout-tip} -->
<!-- Focus on the concepts and ideas, and avoid mathematical details. -->
<!-- ::: -->

<!-- 1. Define a single layer (feed-forward) neural network. -->

<!-- 2. Define a multi-layer (feed-forward) neural network. -->

<!-- 3.  -->


<!-- ### Topic: Entropy (in Information Theory) -->

<!-- ::: {.callout-tip} -->
<!-- Focus on the concepts and ideas, and avoid mathematical details. -->
<!-- ::: -->

<!-- 1. Define the entropy of a random variable. What does it measure? -->



<!-- ### Topic:  -->

<!-- ::: {.callout-tip} -->
<!-- Focus on the concepts and ideas, and avoid mathematical details. -->
<!-- ::: -->

<!-- 1. Define the entropy of a random variable. What does it measure? -->

## Class activity 4

<!-- ### Topic: -->
