---
title: "Class activity work"
code-fold: true
---

```{r}
students <- c("David", "Dibaloke", "Emily", "Tedi", "Alberto", 
              "Caldwell", "Eimienwanlan", "Edward", "Mark", "Adam", 
              "Jennifer", "Josh", "Kathryn", "Clint", "Brigida")
generate_group <- function(all, leader_can, seed, 
                           no_lead1 = 2, no_lead2 = 2, no_mem1 = 6) {
    students <- all
    set.seed(seed)
    lead1 <- sample(leader_can, no_lead1)
    students <- setdiff(students, lead1)
    leader <- setdiff(leader_can, lead1)
    set.seed(seed)
    member1 <- sample(students, no_mem1)
    students <- setdiff(students, member1)
    leader <- setdiff(leader, member1)
    set.seed(seed)
    lead2 <- sample(leader, no_lead2)
    member2 <- setdiff(students, lead2)
    return(list("G1_leader" = lead1,
                "G1_member" = member1,
                "G2_leader" = lead2,
                "G2_member" = member2,
                "leader_can" = setdiff(leader_can, c(lead1, lead2))))
}
```

## Class activity 1

<!-- ::: {.callout collapse="true"} -->
### Topic: Bootstrapping

What is bootstrapping? Why do we use bootstrapping? Please explain it and show how it can be used in simple linear regression, including code demo.

### Resources

Course slides [Simulation-based Inference](https://math4780-f23.github.io/website/slides/11-bootstrap.html#/title-slide) could be helpful. Please collect and prepare your own materials.

### Group 1

```{r}
act1 <- generate_group(all = students, leader_can = students, seed = 6250)
```

#### Leaders:

```{r}
#| echo: false
act1$G1_leader
```

#### Members:

```{r}
#| echo: false
act1$G1_member
```

### Group 2

#### Leaders:

```{r}
#| echo: false
act1$G2_leader
```

#### Members:

```{r}
#| echo: false
act1$G2_member
```

### Knowledge Check

Please go to <https://forms.office.com/r/q7MXBw3raw> to answer the knowledge check questions.

<!-- <https://forms.office.com/r/q7MXBw3raw> -->

### Evaluation

For *leaders*, please go to <https://forms.office.com/r/D2RPbi5VK2> to nominate most engaged members. Note that **you two leaders make one single decision and nominate members jointly**.

For *group members*, please go to <https://forms.office.com/r/WUCKQNJ3Sd> to evaluate your leaders' performance.
<!-- ::: -->

## Class activity 2

<!-- ### Topic: Generalized Additive Models and Generalized Linear Models -->

<!-- 1. Define Generalized Additive Models (GAMs) and Generalized Linear Models (GLMs).  -->

<!-- 2. Why consider using these models? What are the main properties of the two models? What can they do but multiple linear regression can't? -->

<!-- 3. Provide an example or special case of GAM and GLM. -->

<!-- 4. Code demo how to run a GAM and GLM. -->

## Class activity 3

### Topic:

## Class activity 4

### Topic:
